Parity-odd Neutrino Torque Detection

### 2019-03-30 neu_torque.tex
more refs

\section{Discussion}\label{sec.discussion}
We proposed a novel approach to measure the neutrino mass that has not been considered before. 
Two independent observables are compared to infer neutrino mass:
the displacement field measures the inertia tensor on small scales, 
and the neutrino tidal field on large scales.
This is compared to the angular momentum field on the same large scales, 
thus not subject to cosmic variance.
The two fields measure the tides at two different epochs: spin is a fossil of the epoch of galaxy formation.
The applicability relies on the new research studies on the angular momentum connection.
Galaxy formation simulations are needed to study the Lagrangian spin correlations for baryons, 
despite that combining \cite{2010MNRAS.404.1137B,2010MNRAS.405..274H,2011MNRAS.415.2607D,2015ApJ...812...29T,2018arXiv180407306J} and \citep{2002MNRAS.332..325P} already implies a strong correlation. 
We do not propose to use galaxies in clusters, and most spiral galaxies are not in clusters.
%For galaxy clusters, the correlation between minor axes in \cite{2016MNRAS.460.3772S} also implies the correlation between spins. After all, however, since most galaxies are not in clusters so the contribution of clusters is not a major effect.

>>>>

\section{Discussion}\label{sec.discussion}
We proposed a novel approach to measure the neutrino mass that has not been considered before. 
Two independent observables are compared to infer neutrino mass:
the displacement field measures the inertia tensor on small scales, 
and the neutrino tidal field on large scales.
This is compared to the angular momentum field on the same large scales, 
thus not subject to cosmic variance.
The two fields measure the tides at two different epochs: spin is a fossil of the epoch of galaxy formation.
The applicability relies on the new research studies on the angular momentum connection.

From past and current $N$-body simulations, the spin correlation between halos and their Lagrangian protohalos  
(e.g. \citep{2000ApJ...532L...5L,2002MNRAS.332..325P} and this work) is higher than 0.5, 
meaning that the nonlinear effects at low redshifts only add less than 
factor of 2 scatter to the spin correlation.
Recent galaxies formation simulations
(e.g. \cite{2010MNRAS.404.1137B,2010MNRAS.405..274H,2011MNRAS.415.2607D,2015ApJ...812...29T,2018arXiv180407306J}) also show a $\sim 0.5$ spin correlation between galaxies and halos,
and thus baryonic effects also contribute only factor of 2.
These strong correlations are much higher than the $\sim 0.01$ order correlation between galaxy shapes
and true tidal fields by weak lensing observations \citep{2013JCAP...01..026A}. 
We do not propose to use galaxies in clusters, and most spiral galaxies are not in clusters.
%For galaxy clusters, the correlation between minor axes in \cite{2016MNRAS.460.3772S} also implies the correlation between spins. After all, however, since most galaxies are not in clusters so the contribution of clusters is not a major effect.
